skeleton racing with the hyper2 package

### 2025-02-27 inst/curling.Rmd
S3 classes ordertable and ranktable
start work on issue #244

```{r readcurlingtable}
curling_table  <- read.table("curling.txt",header=TRUE)
curling_table
```

@@

```{r,definsupportb,cache=TRUE}
curling1 <- ordertable2supp(ct)
head(curling1)
curling1_maxp <- maxp(curling1)
pie(curling1_maxp)
```

@@

for(i in seq_len(ncol(curling_table))){
    x <- curling_table[,i]
    names(x) <- rownames(curling_table)
    curling2 <- curling2 + ordervec2supp(x[!is.na(x)])
}
head(curling2)
(curling2_maxp <- maxp(curling2))
pie(curling2_maxp)
```

>>>>

```{r readcurlingtable}
curling_table  <- ordertable(read.table("curling.txt",header=TRUE))
curling_table
```

@@

```{r,definsupportb,cache=TRUE}
curling1 <- suppfun(ordertable(ct))
summary(curling1)
curling1_maxp <- maxp(curling1)
pie(curling1_maxp)
```

@@

for(i in seq_len(ncol(curling_table))){
    x <- curling_table[,i]
    names(x) <- rownames(curling_table)
    curling2 <- curling2 + ordervec2supp(x[!is.na(x)])
}
summary(curling2)
(curling2_maxp <- maxp(curling2))
pie(curling2_maxp)
```

### 2025-02-27 inst/skating.Rmd
start work on issue #244

```{r,maxshow, cache = TRUE}
skating <- ordertable2supp(skating_table)
options("use_alabama" = TRUE)
skating_maxp <- maxp(skating,startp=
c(5.0493913251e-06, 0.0053037393083, 0.090240695999, 
0.00036893464900, 1.1397045995e-05, 8.3424027249e-05, 
9.8129903007e-06, 0.00026960143514, 0.29831585124, 
0.001376333090, 2.9434081237e-06, 0.26550514587, 
0.00051946513092, 1.7e-06, 0.00080745068338, 
0.00029358481485, 0.00048852120227, 0.0053075302458, 
0.0025877438737, 0.30889220253, 1.2869403350e-05, 
0.0184563624305147))    # values from previous repeated runs of maxp()
m <- skating_maxp # for ease of  typing
m
```

@@

```{r makelikef}
o <- ordertable2supp(o)
o
```
and have some fun with it:

>>>>

```{r,maxshow, cache = TRUE}
skating <- suppfun(skating_table)
options("use_alabama" = TRUE)
skating_maxp <- maxp(skating,startp=
c(5.0493913251e-06, 0.0053037393083, 0.090240695999, 
0.00036893464900, 1.1397045995e-05, 8.3424027249e-05, 
9.8129903007e-06, 0.00026960143514, 0.29831585124, 
0.001376333090, 2.9434081237e-06, 0.26550514587, 
0.00051946513092, 1.7e-06, 0.00080745068338, 
0.00029358481485, 0.00048852120227, 0.0053075302458, 
0.0025877438737, 0.30889220253, 1.2869403350e-05, 
0.0184563624305147))    # values from previous repeated runs of maxp()
m <- skating_maxp # for ease of  typing
m
```

@@

```{r makelikef}
o <- suppfun(o)
o
```
and have some fun with it:

### 2025-02-27 inst/skeleton.Rmd
start work on issue #244

```{r readskeletontable}
(skeleton_table <- read.table("skeleton2022.txt",header=TRUE))
```

@@

```{r,label=processskeleton,cache=TRUE}
skeleton <- ordertable2supp(skeleton_table)
skeleton_maxp <- maxp(skeleton)
skeleton_maxp
pie(skeleton_maxp)
dotchart(skeleton_maxp)
dotchart(log(skeleton_maxp))
```

>>>>

```{r readskeletontable}
(skeleton_table <- ordertable(read.table("skeleton2022.txt",header=TRUE)))
```

@@

```{r,label=processskeleton,cache=TRUE}
skeleton <- suppfun(skeleton_table)
skeleton_maxp <- maxp(skeleton)
skeleton_maxp
pie(skeleton_maxp)
dotchart(skeleton_maxp)
dotchart(log(skeleton_maxp))
```
